---
title: "RAnalysis"
output: html_notebook
---

1) Background: 
  
The data includes This dataset contains Average Daily Traffic (ADT) counts collected for the City of San Jose for the previous 15 years  ADT values are then given as:  ‘ADT One’ and ‘ADT Two’ which correspond to the ADT collected in the recorded travel directions. ‘ADT’ corresponds to the total ADT which is a sum of ‘ADT One’ and ‘ADT Two.’ Data is published on Mondays on a weekly basis. I was interesting in understanding how the city of San Jose measured the daily traffic and what correlations will be found. 

  - How big is it: 
  8162 rows  13 columns.
  - How many numeric variables: 
  There are  4 numeric variables 
  - How many categorical variables:
  There are  9 categorical variables 
  

```{r}
library(tidyverse)

indata <- read.csv("C:\\Users\\josel\\Documents\\Downloads\\Average_Daily_Traffic.csv")
 
dim (indata)
str (indata)
```

 Are there any missing values?
 There aren't any missing values.
 
  
```{r}
is.data.frame(indata) 

is_tibble(indata)

indata_tibble <- as_tibble(indata)
is_tibble(indata_tibble)

indata_tibble

summary (indata_tibble)


cleaned_data <- na.omit(indata_tibble)

dim(cleaned_data)

print(paste("Number of rows dropped due to missing values: ", dim(indata_tibble)[1] - dim (cleaned_data)[1]))
```
 

1399 ommitted duplicated
 

```{r}
duplicated(indata_tibble)
```




```{r}
summary (indata_tibble)
```


Select one categorical variable, compute these statistics on a numeric variable by grouping on a categorical variable:

categorical variable- Street one and the numerical variable- ADT




```{r}
indata_tibble %>% group_by(STREETONE) %>% summarise( count=n(), avg_ADT
 = mean(ADT), stddev_ADT = sd(ADT), max_Distance= max(ADT), min_Distance= min (ADT))

```

2) Descriptive analysis: 



```{r}
indata_tibble %>% filter(STREETONE == "LEIGH AVE" ) %>% ggplot() + geom_histogram(mapping = aes(x=ADT), binwidth = function(x) 2*IQR(x)/ length(x)^(1/3))

```

 Relationship between variables:

Since R is 0.97 it means that the correlation is linear and positive. 2.2e-16 as the p value would indicate a significant result, meaning that the actual p value is even smaller than 2.2e-16 (a typical threshold is 0.05, anything smaller counts as statistically significant).


```{r}
install.packages("ggpubr")
```

```{r}
library ("ggpubr")
ggscatter(indata_tibble, x="ADTONE", y= "ADTTWO", add= "reg.line", conf.int= TRUE, cor.coef= TRUE, cor.method = "pearson", xlab = "ADTONE", ylab= "ADTTWO")
```


```{r}
cor.test(indata_tibble$ADTONE, indata_tibble$ADTTWO, )
```

3. Hypothesis Testing:

  H0: The two variables are independent.
  H1: The two variables are not independent.

- Since the p-value is less than 0.05, we reject the null hypothesis. This means we have sufficient evidence to say that there is an association between ADTONE and ADTTWO 



```{r}
stu_data= table (indata_tibble$LATITUDE, indata_tibble$LONGITUDE)
print (stu_data)
```
```{r}
chisq.test(stu_data, correct = FALSE)
```

4. Summary: 

The variables displayed correlation and or dependence on each other

In accordance to the Chi Squared test and two tailed hypothesis testing. 
